Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-04-01 ProbabilisticCoherence.tex
Cleaned up definition of basis series and comparison to Ben Taieb Taylor Hyndman definition of coherence

For a particular coherent subspace $\mathbb{C}^m$, there exist several distinct basis vectors. For example, in the small hierarchy considered above, 
 $\{(1 ~1 ~0)', (1 ~0 ~1)'\}$, 
 $\{(1 ~ 0 ~ 1)',(0~1~-\!\!1)'\}$ 
and the singular value decomposition of these two are some alternative basis vectors that span the same $\mathbb{C}^m$. Given a basis for $\mathbb{C}^m$, every series of the hierarchy can be linearly determined as a linear combination of those basis vectors. We refer to the coefficients of these linear combinations as the \textit{basis series}. It is apparent that these basis series are $m$-dimensional and linearly independent in a given hierarchy. For example, in the smallest hierarchy, $(A,B)$ and $(Tot,A)$ are the basis series corresponding to the basis vectors 
 $\{(1 ~1 ~0)', (1 ~0 ~1)'\}$, 
 $\{(1 ~ 0 ~ 1)',(0~1~-\!\!1)'\}$
respectively. Thus it is clear that the set of bottom-level series is a basis series that corresponds to the column vectors of $\bm{S}$.

Because the basis is not unique for a given coherent subspace, Definition~\ref{def:cohprob} is not unique, and one can redefine the coherent probabilistic forecasts with respect to any basis. However, we stick to Definition~\ref{def:cohprob} and consider the basis defined by the columns of $\bm{S}$ in what follows.

Definitions~\ref{def:cohpoint} and~\ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section. In contrast to our definition, \citet{BenTaieb2017} define coherent probabilistic forecasts in terms of convolutions. According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.  While this is consistent with our definition, it is not easy to extend their definition to deal with probabilistic reconciliation.

>>>>

These definitions of the coherent space $\mathfrak{s}$ and coherent point and probabilistic forecasts are defined in terms of the mapping $\bm{S}$ and may give the impression that the bottom level series play an important role in the definition.  However, alternative definitions could be formed using any set of basis vectors that spans $\mathfrak{s}$. For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$.  In this case the matrix $\bm{S}$ has columns  $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$ and the mapping $\bm{S}$ transforms $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.  However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy.  In general, since there are an infinite number linear bases for $\mathfrak{s}$ the definitions above could be made in terms of any series and not just the bottom level series.  In general we will call the series (or linear combinations thereof) used in the definitions of coherence as \textit{basis series}.  Unless stated otherwise, we will always consider the bottom level series to be the basis series, since this facilitates comparison with existing approaches in the literature.

%Because the basis is not unique for a given coherent subspace, Definition~\ref{def:cohprob} is not unique, and one can redefine the coherent probabilistic forecasts with respect to any basis. However, we stick to Definition~\ref{def:cohprob} and consider the basis defined by the columns of $\bm{S}$ in what follows.

%Definitions~\ref{def:cohpoint} and~\ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section. 
To  the best of our knowledge, the only other definition of coherent probabilistic forecasts is given by \citet{BenTaieb2017} who define coherent probabilistic forecasts in terms of convolutions. According to their definition, probabilistic forecasts are coherent when a convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.  Their definition is consistent with our definition, our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of probabilistic forecast reconciliation to which we now turn our attention.
